### 2023-04-29 tex/annexes_sms.tex
No colored links in toc
Up conclusion

\chapter{Submeso-color: code}
\selectlanguage{english}

@@

date is a YYYY/MM[/DD] format argument. The `/' separator can also be `-', a space, or nothing.
\lit{args['date_str']} is a tuple of the strings of year, month, and eventually day\@. \lit{args['date']} stores a datetime object.

@@

You may have noticed that the function described in \titleref{sec:org-created-funcs} have the following signature \py{(args: Dict = None, **kwargs: Any)}.
Thoses functions process thoses arguments using \py{lib.data.process_args(args_names, args, replace_defaults=None, **kwargs)}.
The idea is that we define the arguments the function *needs* with \lit{args_names}.
We then supply both args and kwargs. From those are only kept the needed arguments.
If arguments are missing a default value is used (either defined with \lit{/lib/conf.ini} or \lit{replace_defaults}).
Arguments found in kwargs will replace those from \lit{args}.
Users should not need to use \lit{lib.data.process_args} directly, argument processing is done automatically on functions defined by \hyperref[sec:org-datasets]{dataset creation}.

@@

\subsection{Module file}
To load a dataset in memory, its corresponding python file can be used. It can be found in \lit{lib/data/[module].py}.
In those files are defined some basic information about the data.
\lit{lib.data.create_dataset()} is then used to automatically create a number of functions that can be used to access the data.
\subsubsection{The basic information}
\paragraph{Arguments names / Dataset parameters}
Each dataset can depend on different parameters, set dynamically when calling functions (see \titleref{sec:org-args}).
The list of argument names used by the dataset must be supplied as a set.
Typically:
\begin{python}
ARGS = {'region', 'days'}
\end{python}
/ie/ the region, and the temporal resolution.
Datasets are typically available daily, as n-days average, or as climatology.
Each variation has its own subfolder of form `1days', `\{n\}days', `climato'.
For more on the climatology, see \linkfile{docs/climato.html}{docs/climato.html}.

>>>>

\chapter{Submeso-color: extrait de la documentation}
\label[appendix]{ax:sms-doc}
\selectlanguage{english}

@@

date is a \lit{YYYY/MM[/DD]} format argument. The `/' separator can also be `-', a space, or nothing.
\lit{args['date_str']} is a tuple of the strings of year, month, and eventually day\@. \lit{args['date']} stores a datetime object.

@@

You may have noticed that the function described in \titleref{sec:org-created-funcs} have the following signature \py{(args: Dict = None, **kwargs: Any)}.
Thoses functions process thoses arguments using \py{lib.data.process_args(args_names, args, replace_defaults=None, **kwargs)}.
The idea is that we define the arguments the function \textbf{needs} with \lit{args_names}.
We then supply both args and kwargs. From those are only kept the needed arguments.
If arguments are missing a default value is used (either defined with \lit{/lib/conf.ini} or \lit{replace_defaults}).
Arguments found in kwargs will replace those from \lit{args}.
Users should not need to use \lit{lib.data.process_args} directly, argument processing is done automatically on functions defined by \hyperref[sec:org-datasets]{dataset creation}.

@@

\subsection{Module file}
To load a dataset in memory, its corresponding python file can be used. It can be found in \lit{lib/data/[module].py}.
In those files are defined some basic information about the data.
\lit{lib.data.create_dataset()} is then used to automatically create a number of functions that can be used to access the data.
\subsubsection{The basic information}
\paragraph{Arguments names / Dataset parameters}
Each dataset can depend on different parameters, set dynamically when calling functions (see \titleref{sec:org-args}).
The list of argument names used by the dataset must be supplied as a set.
Typically:
\begin{python}
ARGS = {'region', 'days'}
\end{python}
ie the region, and the temporal resolution.
Datasets are typically available daily, as n-days average, or as climatology.
Each variation has its own subfolder of form `1days', `\{n\}days', `climato'.
For more on the climatology, see \linkfile{docs/climato.html}{docs/climato.html}.

### 2023-04-29 tex/conclusion.tex
up
Up
Replace subfiles by includeonly
taken care of by makefile
Move ref software in backmatter
Better layout & commands
Remove gls command for hi and sst
Up intro
Up perspectives
Up conclusion

\documentclass[index]{subfiles}
\begin{document}

@@

\end{document}

>>>>

% chktex-file 13

@@

Dans le cadre de cette thèse, grâce à 20~années de données satellites nous avons montré et \emph{quantifié} l'impact des fronts sur la \al{chl} dans l'Atlantique Nord autour du Gulf Stream, selon la saison et la biorégion concernée.
Nous réaffirmons l'augmentation \emph{locale} de la \al{chl} dans les fronts par rapport à l'environnement avoisinant.
Cet excès local est d'autant plus élevé que \emph{l'intensité des fronts} est importante.
Il est particulièrement important immédiatement autour du Gulf Stream (\pct{+60} en moyenne), ainsi que pendant le bloom printanier (où il atteint \pct{+150}).

En revanche, en calculer le surplus de \al{chl} à \emph{l'échelle de la biorégion} \encadra{en donc en comptabilisant la \emph{surface occupée} par les fronts} cette est augmentation est moins spectaculaire (inférieur à \pct{+5}).
Ce surplus est de valeur comparable pour les fronts de fortes et de faible intensité, ces derniers ayant un impact local moindre mais compensent par une plus importante surface occupée.

Dans le biome subpolaire, nous apportons des preuves observationnelles que le démarrage du bloom se fait plus tôt dans les fronts que dans le reste de la zone \encadra*{de deux semaines environ}.
Ce résultat constitue une première observation directe et quantification de ce phénomène.

peut être utilisé pour une paramétrisation dans un OGCM/ESM et des projections climatiques.

Au delà de ces résultats, nous fournissons une méthode de calcul des fronts validée.
Nous reconnaissons que malgré l'importance et les potentielles applications de la détection des fronts, il n'existe pas encore d'outils ou de produits facilitant leur utilisation scientifique.
Sans fournir y une solution définitive nous avons néanmoins pu mieux en délimiter la forme.
À la fois en termes des algorithmes potentiellement utile et de leur validation régionale, ainsi que des outils qui permettrait leur implémantation, et leur application sur des données satellites, diverses et parfois de large volume.

\fancybreakdisplay

### 2023-04-29 tex/intro.tex
Up conclusion

\begin{tcolorbox}[
  enhanced,
  frame hidden, interior hidden,
  borderline={1.pt}{3pt}{black}, arc=2.mm,
  borderline north={1.2pt}{0pt}{black},
  borderline south={1.2pt}{0pt}{black},
  borderline west={1.2pt}{0pt}{black},
  borderline east={1.2pt}{0pt}{black},
  top=2\onelineskip,
  bottom=2\onelineskip,
  ]
  \begin{list}{}{
      \setlength{\labelsep}{0.5em}
      \setlength{\itemindent}{0pt}
      \setlength{\leftmargin}{2em}
      \setlength{\labelwidth}{0.5em}
      \setlength{\listparindent}{0pt}
      \setlength{\parsep}{\parskip}
      \setlength{\itemsep}{\onelineskip}
      \setlength{\topsep}{\onelineskip}
      \renewcommand*\makelabel[1]{\adfrightarrowhead}}
    \item Comment quantifier la réponse de la \al{chl} aux dynamiques frontales dans la région du Gulf Stream ?
    \item Comment est-ce que l'augmentation de \al{chl} dans les fronts est conditionnée par leur intensité ?
    \item Peut-on détecter un bloom précoce dans les fronts depuis des données satellites ?
  \end{list}
\end{tcolorbox}

>>>>

\begin{tcolorbox}[
  enhanced,
  frame hidden, interior hidden,
  borderline={1.pt}{3pt}{black}, arc=2.mm,
  borderline north={1.2pt}{0pt}{black},
  borderline south={1.2pt}{0pt}{black},
  borderline west={1.2pt}{0pt}{black},
  borderline east={1.2pt}{0pt}{black},
  top=2\onelineskip,
  bottom=2\onelineskip,
  left=1.2em, right=1.2em,
  ]
  \begin{list}{}{
      \setlength{\labelsep}{0.5em}
      \setlength{\itemindent}{0pt}
      \setlength{\leftmargin}{0pt}
      \setlength{\labelwidth}{0.5em}
      \setlength{\listparindent}{0pt}
      \setlength{\parsep}{\parskip}
      \setlength{\itemsep}{\onelineskip}
      \setlength{\topsep}{\onelineskip}
      \renewcommand*\makelabel[1]{\adfrightarrowhead}}
    \item Comment quantifier la réponse de la \al{chl} aux dynamiques frontales dans la région du Gulf Stream ?
    \item Comment est-ce que l'augmentation de \al{chl} dans les fronts est conditionnée par leur intensité ?
    \item Peut-on détecter un bloom précoce dans les fronts depuis des données satellites ?
  \end{list}
\end{tcolorbox}
